Outline--Draft JCP format for: Reactive Force Field for Perovskite--Based Solid Oxides and Its Application to Solid Oxide Electrolysis Cells

### 2019-05-17 Paper/paper.tex
References added
Three references used in introduction

@@

\subsection{ReaxFF and Parameterization Strategy}

@@

\subsection{Electronic Structure Calculations for Dataset Generation}

@@

\subsection{Molecular Dynamics Trajectories Using ReaxFF}

@@

\section{Results and Discussion}

@@

\section{Applications and Discussion}

@@

\section{Concluding Remarks}

>>>>

% introduce lanthanum uses
Lanthanum is a transition metal involved in various applications that range from use in catalysts, batteries, and in medicine \cite{atwood2013rare,he2013preparation}.
Particularly, catalysts based on Lanthanum oxide have shown a good efficiency in the oxidative coupling of methane to form ethane and/or ethylene \textbf{import citation}, or as main components of electro--catalysts used in CO$_2$ conversion to CO \textbf{import citation}.

% what is the problem with lanthanum
\emph{need to introduce more about uses of La}

Quantum mechanical calculations have been carried out to understand the role and influence, if any, of Lanthanum on its many applications.
However, many of the phenomena that takes place in catalysis involve the interaction of many atoms for which rigorous quantum mechanical calculations are unfeasible.
For this reason, force fields are commonly used to study applications via molecular dynamics calculations.
In particular, the behaviour of La$^3+$ in aqueous solution has been studied by various groups using different parametrization strategies to improve the accuracy of the description of the interaction between Lanthanum and water \cite{duvail2007pair}.
These approaches have proven to successfully describe the La--O interaction in liquid water, but due to the size of Lanthanum the introduction of some form of explicit polarizability is necessary to properly describe the interactions between Lanthanum and other elements.

One of the major drawbacks of the use of general polarizable force fields is the impossibility to describe chemical reactions, as these models disable explicit bond breaking and formation to produce transferable parameters and simple expressions for calculating energies and forces.
But, with the increasing computational power processing, reactive force fields that can capture bond breaking and formation on--the--fly have been developed actively during the last decade.
Particularly, ReaxFF is a reactive force field that has been extensively used to study successfully reactive events between solid, liquid, and gas phases.
This transferability between phases, and the possibility to study phenomena where chemical events and dynamical factors are of importance makes ReaxFF a powerful tool that bridges the lower computational expense from force fields and the quantum mechanical description of a system.
Although the current form of ReaxFF has been in development since 2008 \cite{chenoweth_reaxff_2008} and many elements have been parametrized to be used in ReaxFF not all interactions have been fully parametrized, and some elements still remain to be parametrized.
An important point is that parameters used in ReaxFF are heavily dependent on the applications for which they have been explicitly parametrized, so while some parameters can be transferable testing is necessary to ensure that interactions are well described.

The purpose of this study is to generate a set of parameters for Lanthanum as well as its interaction with other elements, namely Ca, Fe, Cr, and O, to be used for describing solid state materials used in catalysis.
To this end, in the remainder of this paper, we introduce ReaxFF and a parametrization strategy in Sec.~\ref{sec:reaxff-strategy}; and the computational methods used, i.e. electronic structure calculations in Sec.~\ref{sec:dft-details}; and molecular dynamics simulations in Sec.~\ref{sec:md-details}.
Then, we discuss in Sec.~\ref{sec:results-and-discussion} the quality of the newly generated parameters by analyzing the ability of the ReaxFF to reproduce the generated dataset from quantum mechanical calculations.
Finally, we use the parameters obtained to model some possible applications discuss the results in Sec.~\ref{sec:applications}, and present our concluding remarks in Sec.~\ref{sec:conclusions}

@@

\subsection{ReaxFF and Parameterization Strategy}
\label{sec:reaxff-strategy}

@@

\subsection{Electronic Structure Calculations for Dataset Generation}
\label{sec:dft-details}

@@

\subsection{Molecular Dynamics Trajectories Using ReaxFF}
\label{sec:md-details}

@@

\section{Parametrization Results and Discussion}
\label{sec:results-and-discussion}

@@

\section{Applications}
\label{sec:applications}

@@

\section{Concluding Remarks}
\label{sec:conclusions}
